%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{latin}

\begin{thebibliography}{99}
\thispagestyle{empty}
%\begin{latin}
%===============+===============
\bibitem{Ref28BSYXZ}
Bu, W. P., Shu, S., Yue, X. Q., Xiao, A. G., \& Zeng, W.  
(2019).
Space–time finite element method for the multi-term time-space fractional diffusion equation on a two-dimensional domain.
\textit{Comput. Math. Appl., 78}.
1367–1379.

%===============+===============
\bibitem{Ref21BTY}
Bu, W. P., Tang, Y. F., \& Yang, J. Y.
(2014).
Galerkin finite element method for two-dimensional Riesz space fractional diffusion equations.
\textit{J. Comput. Phys., 276}.
26–38.

%===============+===============
\bibitem{Ref24BTWY}
Bu, W. P., Tang, Y. F., Wu, Y. C., \& Yang, J. Y.
(2015).
Crank–Nicolson ADI Galerkin finite element method for two-dimensional fractional FitzHugh–Nagumo monodomain model.
\textit{Appl. Math. Comput., 257}.
355–364.

%===============+===============
\bibitem{Ref48CLZ}
Chen, H., Lv, W., \& Zhang, T. T.
(2018).
A Kronecker product splitting preconditioner for two-dimensional space-fractional diffusion equations.
\textit{J. Comput. Phys., 360}.
1–14.

%===============+===============
\bibitem{Ref15CDL}
Cheng, X. J., Duan, J. Q., \& Li, D. F.
(2019).
A novel compact ADI scheme for two-dimensional Riesz space fractional nonlinear reaction–diffusion equations.
\textit{Appl. Math. Comput., 346}.
452–464.

%===============+===============
\bibitem{Ref4DXL}
Ding, Z., Xiao, A., \& Li, M.
(2010).
Weighted finite difference methods for a class of space fractional partial differential equations with variable coefficients.
\textit{Journal of Computational and Applied Mathematics, 233}(8).
1905-1914.

%===============+===============
\bibitem{Ref57DKPS}
Dobrev, V. A., Kolev, Tz.,  Petersson, N. A., \& Schroder, J. B. 
(2017).
Two-level convergence theory for multigrid reduction in time (MGRIT).
\textit{SIAM Journal on Scientific Computing, 39}(5).
S501–S527.

%===============+===============
\bibitem{Ref20ER}
Ervin, V. J., \& Roop, J. P.
(2006).
Variational formulation for the stationary fractional advection dispersion equation.
\textit{Numer. Methods Partial Differential Equations, 22}.
558–576.

%===============+===============
\bibitem{Ref113E}
Evans, L. C.
(2010).
\textit{Partial differential equations} (2nd Ed.).
AMS.

%===============+===============
\bibitem{Ref52FFKMS}
Falgout, R. D., Friedhoff, S., Kolev, T. V., Maclachlan, S. P., \& Schroder, J. B.
(2012).
Parallel time integration with multigrid.
\textit{SIAM Journal on Scientific Computing, 36}(6).
635–661.

%===============+===============
\bibitem{Ref103FLW}
Falgout, R. D., Lecouvez, M., \& Woodward, C. S.
(2019).
A parallel-in-time algorithm for variable step multistep methods.
\textit{Journal of Computational Science, 37}.
101029.

%===============+===============
\bibitem{Ref105FMOS}
Falgout, R. D., Manteuffel, T. A., O'Neill, B., \& Schroder, J. B.
(2017).
Multigrid reduction in time for nonlinear parabolic problems: a case study
\textit{SIAM Journal on Scientific Computing, 39}(5).
S298-S322.

%===============+===============
\bibitem{Ref112FZLTG}
Feng, L. B., Zhuang, P., Liu, F., Turner, I., \& Gu, Y. T.
(2016).
Finite element method for space-time fractional diffusion equation
\textit{Numerical Algorithms, 72}.
749-767.

%===============+===============
\bibitem{Ref14FZLTAL}
Feng, L. B., Zhuang, P., Liu, F., Turner, I., Anh, V., \& Li, J.
(2017).
A fast second-order accurate method for a two-sided space-fractional diffusion equation with variable coefficients.
\textit{Computers \& Mathematics with Applications, 73}(6).
1155-1171.

%===============+===============
\bibitem{Ref108FW}
Fox, W. P., \& West, R. D.
(2025).
\textit{Numerical methods and analysis with mathematical modelling}.
CRC Press.

%===============+===============
\bibitem{Ref101FFKMS}
Friedhoff, S., Falgout, R. D., Kolev, T. V., Maclachlan, S. P., \& Schroder, J. B.
(2014).
A multigrid-in-time algorithm for solving evolution equations in parallel.
\textit{Lawrence Livermore National Laboratory}.

%===============+===============
\bibitem{Ref61G}
Gander, M. J.
(2015).
50 years of time parallel time integration.
\textit{Contrib. Math. Comput. Sci., 9}.
69–114.

%===============+===============
\bibitem{Ref55GV}
Gander, M. J., \& Vandewalle, S.
(2007).
Analysis of the Parareal Time Parallel Time Integration Method.
\textit{SIAM Journal on Scientific Computingm, 29}(2).
556-578.

%===============+===============
\bibitem{Ref107G}
Gockenbach, G. S.
(2006).
\textit{Understanding and implementing the finite element method}.
SIAM.

%===============+===============
\bibitem{Ref49GBT}
Gong, C. Y., Bao, W. M., \& Tang, G. J.
(2013).
A parallel algorithm for the Riesz fractional reaction–diffusion equation with explicit finite difference method.
\textit{Fract. Calc. Appl. Anal., 16}.
654–669.

%===============+===============
\bibitem{Ref42GBTJL}
Gong, C. Y., Bao, W. M., Tang, G. J., Jiang, Y. W., \& Liu, J.
(2015).
Computational challenge of fractional differential equations and the potential solutions: a survey.
\textit{Math. Probl. Eng., 2015}.
258–265.

%===============+===============
\bibitem{Ref114GGS}
Günther, S., Gauger, N. R., \&  Schroder, J. B.
(2018).
A non-intrusive parallel-in-time adjoint solver with the XBraid library.
\textit{Comput. Visual Sci., 19}.
85–95.

%===============+===============
\bibitem{Ref9HFCS}
Hao, Z. P., Fan, K., Cao, W. R., \& Sun, Z. Z. 
(2016).
A finite difference scheme for semilinear space-fractional diffusion equations with time delay.
\textit{Appl. Math. Comput., 275}.
238–254.

%===============+===============
\bibitem{Ref0HSNRFS}
Hessenthaler, A., Southworth, B. S., Nordsletten, D., R\"{o}hrle, O., Falgout, R. D., \& Schroder, J. B.
(2020).
Multilevel convergence analysis of Multigrid reduction-in-time.
\textit{SIAM Journal on Scientific Computing, 42}(2).
A771-A796.

%===============+===============
\bibitem{Ref63Hypre}
HYPRE: Scalable linear solvers and multigrid methods, 
\href{https://llnl.gov/casc/hypre}{\cod{https://llnl.gov/casc/hypre}}.

%===============+===============
\bibitem{Ref31JW}
Jia, J. H., \& Wang, H.
(2016).
A fast finite volume method for conservative space-fractional diffusion equations in convex domains.
\textit{J. Comput. Phys., 310}.
63–84.

%===============+===============
\bibitem{Ref109J}
Jin, B.
(2021).
\textit{Fractional differential equations: an approach via fractional derivatives}.
Springer.

%===============+===============
\bibitem{Ref51LMT}
Lions, J. L., Maday, Y., \& Turinici, G.
Résolution D’EDP par un schéma en tempspararéel.
\textit{C. R. Math. Acad. Sci. Paris 332}.
(2001).
661–668.

%===============+===============
\bibitem{Ref30LZTBA}
Liu, F., Zhuang, P., Turner, I., Burrage, K., \& Anh, V.
(2014).
A new fractional finite volume method for solving the fractional diffusion equation.
\textit{Appl. Math. Model., 38}.
3871–3878.

%===============+===============
\bibitem{Ref59N}
Nievergelt, J.
(1964).
Parallel methods for integrating ordinary differential equations.
\textit{Commun. ACM, 7}.
731–733.

%===============+===============
\bibitem{Ref43PS}
Pang, H. K., \& Sun, H. W.
(2012).
Multigrid method for fractional diffusion equations.
\textit{J. Comput. Phys., 231}.
693–703.

%===============+===============
\bibitem{Ref111R}
Reddy, B. D.
(1998).
\textit{Introductory functional analysis: with applications to boundary value problems and finite elements}.
Springer.

%===============+===============
\bibitem{Ref106RTW}
Ries, M., Trottenberg, U., \& Winter, G.
(1983).
A note on MGR methods.
\textit{Linear Algebra and its Applications, 49}.
1–26.

%===============+===============
\bibitem{Ref33SX}
Song, F. Y.,\& Xu, C. J.
(2015).
Spectral direction splitting methods for two-dimensional space fractional diffusion equations.
\textit{J. Comput. Phys., 299}.
196–214.

%===============+===============
\bibitem{Ref100SB}
Stoer, J., \& Bulirsch, R.
(2002).
\textit{Introduction to Numerical Analysis} (3rd ed.).
Springer.

%===============+===============
\bibitem{Ref110SG}
Sun, Z. Z., \& Gao, G. H.
(2020).
\textit{Fractional differential equations: Finite difference methods}.
De Gruyter.

%===============+===============
\bibitem{Ref102TMV}
Tielen, R., Möller, M., \& Vuik, C.
(2022).
Combining p-multigrid and MGRIT methods to obtain a scalable solver for Isogeometric Analysis.
\textit{SN Appl. Sci., 4}(163).

%===============+===============
\bibitem{Ref115TOS}
Trottenberg, U., Oosterlee, C., \& Schüller, A.
(2001).
\textit{Multigrid}. 
Academic Press, San Diego.

%===============+===============
\bibitem{Ref50WLGZX}
Wang, Q. L., Liu, J., Gong, C. Y., Zhang, Y., \& Xing, Z. C.
(2015).
A GPU-based fast solution for Riesz space fractional reaction–diffusion equation.
\textit{Proc. 18th Intl. Conf. Network-Based Info. Sys.}
317–323.

%===============+===============
\bibitem{Ref54WZ}
Wu, S. L., \& Zhou, T.
(2017).
Fast parareal iterations for fractional diffusion equations.
\textit{J. Comput. Phys., 329}.
210–226.

%===============+===============
\bibitem{Ref56XBraid}
XBraid: Parallel time integration with multigrid, 
\href{https://llnl.gov/casc/xbraid}{\cod{https://llnl.gov/casc/xbraid}}.

%===============+===============
\bibitem{Ref104XZ}
Xu, J., \& Zikatanov, L.
(2017).
Algebraic multigrid methods.
\textit{Acta Numerica, 26}.
591–721.

%===============+===============
\bibitem{Ref34Y}
Yang, Y.
(2015).
Jacobi spectral Galerkin methods for fractional integro-differential equations.
\textit{Calcolo, 52}.
519–542.

%===============+===============
\bibitem{Ref25YYNWZL}
Yang, Z., Yuan, Z., Nie, Y., Wang, J., Zhu, X., \& Liu, F.
(2019).
Finite element method for nonlinear Riesz space fractional diffusion equations on irregular domains.
\textit{J. Comput. Phys., 330}.
863–883.

%===============+===============
\bibitem{Ref0YSXBP}
Yue, X., Shu, S., Xu, X., Bu, W., \& Pan, K.
(2019).
Parallel-in-time multigrid for space–time finite element approximations of two-dimensional space-fractional diffusion equations.
\textit{Comput. Math. Appl., 78}.
3471–3484.

%===============+===============
\bibitem{Ref21BTYRef29ZLA}
Zhang, H., Liu, F., \& Anh, V.
(2010).
Galerkin finite element approximation of symmetric space-fractional partial differential equations
\textit{Appl. Math. Comput., 217}.
2534-2545.

%===============+===============
\bibitem{Ref26ZBZT}
Zhao, Y., Bu, W. P., Zhao, X., \& Tang, Y. F.
(2017).
Galerkin finite element method for two-dimensional space and time fractional Bloch-Torrey equation.
\textit{J. Comput. Phys., 350}.
117–135.

%===============+===============
%\end{latin}

\end{thebibliography}

\end{latin}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
